Species motif participation provides unique information about species risk of extinction

### 2023-04-14 manuscript/JAE_reply.tex

            \textbf{R:} Yes, a binomial error distribution would be more appropriate. We have corrected the error and updated our results accordingly and thank the Reviewer for pointing this out. [[something about what changed, if anything]]

@@

            \item Introduction Line 13-16: The wording here makes it seem like species loss is both the stressor/disturbance and the response variable. This would be clearer if the authors clarify whether they are studying the effects of disturbance at the primary producer level on consumer persistence right away. It wouldalso be helpful to define exactly what definition of disturbance they are referring to in the introduction.

>>>>

            \textbf{R:} Yes, a binomial error distribution would be more appropriate. We have corrected the error and updated our results accordingly and thank the Reviewer for pointing this out. Our results were not strongly affected by this change in statistical methodology, except that the relationship between network size and average consumer persistence was no longer significant.

@@

            \item Introduction Line 13-16: The wording here makes it seem like species loss is both the stressor/disturbance and the response variable. This would be clearer if the authors clarify whether they are studying the effects of disturbance at the primary producer level on consumer persistence right away. It would also be helpful to define exactly what definition of disturbance they are referring to in the introduction.
